Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-03-09 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added last citations to pres

\begin{itemize_2pt}
	\item Heterogeneity in mgmt practices across mid-sized and large firms \textcolor{camel}{\citep{Bloom2007, Bloom2010, Syverson2011}}
\end{itemize_2pt}
\end{frame}

@@

%------------------------------------------------
\begin{frame}
\frametitle{A Growing Focus on Management}
\begin{itemize_2pt}
\item \textcolor{bdf}{Classroom Training}: \textcolor{camel}{Field, et al. (2010), Karlan \& Valdivia (2011), Bruhn \& Zia (2013), McKenzie \& Woodruff (2014, 2017), Bulte et al. (2017), Anderson, Chandy, \& Zia (2018), Lafortune et al. (2018)}
\vspace{0.1in}
\item \textcolor{bdf}{Consulting}: \textcolor{camel}{Bloom, et al. (2013), Karlan et al (2015), Bruhn, Karlan, \& Schoar (2019)}
\vspace{0.1in}

\item \textcolor{bdf}{Mobilizing Peer Knowledge}:
    \begin{itemize_2pt}
    \item \textcolor{camel}{Brooks et al. (2018)} $\rightarrow$ Local mentors (market information)
    \item \textcolor{camel}{Cai \& Szeidl (2018)} $\rightarrow$ Business meetings
    \item \textcolor{camel}{Abebe et al. (2019)} $\rightarrow$ Management experience matching
    \end{itemize_2pt}
    \vspace{0.1in}
\end{itemize_2pt}
\end{frame}

\subsection{Our Approach}
\begin{frame}
\frametitle{Harnessing Cross-Firm Heterogeneity}
Some stylized facts about business practices in small firms
\begin{itemize_2pt}
	\item Vast heterogeneity in business practices and performance across similar businesses \citep{deMel2009}
	\item Variation in practices accounts for up to 30\% of variation in TFP across plants within the same firm in the US \citep{Bloom2019}
	\item[] $\rightarrow$ Research has largely overlooked this heterogeneity in program design and implementation
\end{itemize_2pt}

@@

Two complementary behavioral interventions
	\begin{itemize_2pt}
		\item Movie of successful peers
		\begin{itemize_2pt}
			\item \textcolor{bdf}{Psychological and emotional involvement}
			\item[] $\rightarrow$ Social learning through \textcolor{bdf}{observing experiences of similar others}
			\item \textcolor{camel}{Bernard, et al. (2014); La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013)}
		\end{itemize_2pt}

		\item On-site assistance
			\begin{itemize_2pt}
				\item \textcolor{bdf}{Hands-on involvement}
				\item[] $\rightarrow$ Social learning through own \textcolor{bdf}{idiosyncratic experience} \textcolor{camel}{(Kolb, 1984)}
				\item Facilitated by local lay person
			\end{itemize_2pt}
		\item[] $\rightarrow$ Movie and assistance based exclusively on handbook!

@@

\begin{frame}
\frametitle{Handbook Content}

\begin{figure}[htbp]
	\centering
		\includegraphics[width=2.6in]{pics/Handbook_stepbystep.jpg}

@@

\textcolor{bdf}{No significant} impacts on:
    \begin{itemize_2pt}
    \vspace{0.1in}
    \item Business expenses
    \vspace{0.1in} 		
    \item Business size
      \vspace{0.1in}
    \item Number of employees
      \vspace{0.1in}
    \item Number of customers
       \vspace{0.1in}
     \item Business credit
    \end{itemize_2pt}

@@

\appendix
\begin{frame}[label=references, allowframebreaks]
\frametitle{References}
\bibliographystyle{chicago}
\bibliography{businessTraining}
\end{frame}

\section*{\textbf{APPENDIX}}

>>>>

\begin{itemize_2pt}
	\item Heterogeneity in mgmt practices across mid-sized and large firms \citep{Bloom2007, Bloom2010, Syverson2011}
\end{itemize_2pt}
\end{frame}

@@

%------------------------------------------------
\begin{frame}
\frametitle{A Growing Focus on Management}
\begin{itemize_2pt}
\item \textcolor{bdf}{Classroom Training}: \citet{McKenzie2014, Karlan2011, Bruhn2013, Anderson2018, Bulte2017, Field2010}
\vspace{0.1in}
\item \textcolor{bdf}{Consulting}:\citet{Bruhn2018, Anderson2020, Karlan2015}
\vspace{0.1in}

\item \textcolor{bdf}{Mobilizing Peer Knowledge}:
    \begin{itemize_2pt}
    \item \citet{Brooks2018} $\rightarrow$ Local mentors (market information)
    \item \citet{Cai2018} $\rightarrow$ Business meetings
    \item \citet{Abebe2019} $\rightarrow$ Management experience matching
    \end{itemize_2pt}
    \vspace{0.1in}
\end{itemize_2pt}
\end{frame}

\subsection{Our Approach}
\begin{frame}
\frametitle{Harnessing Cross-Firm Heterogeneity}
Some stylized facts about business practices in small firms
\begin{itemize_2pt}
	\item Vast heterogeneity in business practices and performance across similar businesses \citep{McKenzie2017, deMel2009}
	\item Variation in practices accounts for up to 30\% of variation in TFP across plants within the same firm in the US \citep{Bloom2019}
	\item[] $\rightarrow$ Research has largely overlooked this heterogeneity in program design and implementation
\end{itemize_2pt}

@@

Two complementary behavioral interventions
	\begin{itemize_2pt}
		\item Movie of successful peers
		\begin{itemize_2pt}
			\item \textcolor{bdf}{Psychological and emotional involvement}
			\item[] $\rightarrow$ Social learning through \textcolor{bdf}{observing experiences of similar others}
			\item[] \quad \citep[see,e.g.,][]{Bernard2014, Ferrara2012, Chong2009, Berg2017}
		\end{itemize_2pt}

		\item On-site assistance
			\begin{itemize_2pt}
				\item \textcolor{bdf}{Hands-on involvement}
				\item[] $\rightarrow$ Social learning through own \textcolor{bdf}{idiosyncratic experience}
				\item Facilitated by local lay person
			\end{itemize_2pt}
		\item[] $\rightarrow$ Movie and assistance based exclusively on handbook!

@@

%\begin{frame}
%\frametitle{Handbook Content}

%\begin{figure}[htbp]
%	\centering
%		\includegraphics[width=2.6in]{pics/Handbook_stepbystep.jpg}

%	\label{height}
%\end{figure}
%\end{frame}

@@

\textcolor{bdf}{No significant impacts} on:
    \begin{itemize_2pt}
    \vspace{0.1in}
    \item Business expenses
    \vspace{0.1in} 		
    \item Business size
      \vspace{0.1in}
    \item Number of employees
      \vspace{0.1in}
    \item Number of customers
       \vspace{0.1in}
     \item Business credit
    \end{itemize_2pt}

@@

\appendix
\begin{frame}[allowframebreaks] %label=references, 
\frametitle{References}
\bibliographystyle{chicago}
\bibliography{businessTraining}
\end{frame}

\section*{\textbf{Appendix}}
